They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-21 paper/paper.Rmd
start paper discussion

cod_o_win_prop <- cod_rounds |> 
  filter(is_offense) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop)

@@

The empirical offensive round win percentage across all rounds is 47.8%.[^7] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e. the number of round wins by each team prior to an upcoming round). Offensive round win rate is not quite constant, although never veers more than 10% from this global average.

@@

cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 2L:3L) |>
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_k_wins_i_rounds)
  ) |>
  unnest(data)
cod_round_win_prop_after_k_wins_i_rounds |> filter(win_round, notional_p_value < 0.05)
```

@@

>>>>

cod_o_win_prop <- cod_rounds |> 
  filter(is_offense) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop)
cod_o_win_prop^2 * (1 - cod_o_win_prop)
cod_o_win_prop * (1 - cod_o_win_prop)^2

@@

The empirical offensive round win percentage across all rounds is $\phi_O$ = 47.8%.[^7] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e. the number of round wins by each team prior to an upcoming round). Offensive round win rate is not quite constant, although never veers more than 10% from this global average.

@@

tibble(win_streak = 1L) |>
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_k_wins_i_rounds)
  ) |>
  unnest(data) |> 
  filter(win_round, notional_p_value < 0.05)

cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 1L:3L) |>
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_k_wins_i_rounds)
  ) |>
  unnest(data)
cod_round_win_prop_after_k_wins_i_rounds |> 
  filter(notional_prop < prop, notional_p_value < 0.05) |> 
  filter(n_rounds == round) |> 
  filter(win_streak == 1) |> 
  group_by(n_rounds, round) |> 
  mutate(
    total = sum(n),
    prop = n / total
  )
```

@@

# Discussion

For the sake of brevity, I did not delve into win rates and streaks split by offensive or defensive role. For example, it would be interesting to look at whether the round win rate is higher after a streaks of three round wins when the team starts the streak winning as the offensive team. This would mean that, in the round immediately following the streak, the streaking team would be playing defense, where teams are slightly more likely to win on average. On the other hand, streaks of three starting with an offensive round win---theoretically, given $\phi_O$ = 47.7% the expected frequency is $\phi_O^2 \times (1 - \phi_O) \approx 0.119$---are likely to occur less frequently than such streaks starting with a defensive win---$\phi_O \times (1 - \phi_O)^2 \approx 0.130$---so I would want to account for sample size differences.

# Acknowledgements {.unnumbered}

I would like to thank my brother Andrew for giving me feedback on early iterations of this paper, and for requiring me to mention him.
